FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-10-12 NewVersion/sections/Overview.tex

>>>>

\begin{figure*}[t]
	\vspace{-1ex}
	\hspace{-15pt}\begin{tabular}{clclcl}
		&\multicolumn{1}{c}{\includegraphics[width=1.5cm]{pics/P1.pdf}} & &
		\multicolumn{1}{c}{\includegraphics[width=1.5cm]{pics/P2.pdf}} & &
		\multicolumn{1}{c}{\includegraphics[width=1.5cm]{pics/P3.pdf}} \\
		(a) & $\mbody(m,C,A) = (A,...)$\ \ \  & (b) & $\mbody(m,C,A) = (C,...)$\ \ \  & (c) & $\mbody(m,C,A) = (C,...)$ \\
		& $\mbody(m,C,B) = (B,...)$ & & $\mbody(m,C,B) = (C,...)$ & & $\mbody(m,C,B) = (B,...)$ \\
		& $\mbody(m,C,C) = \keyword{undefined}$ & & $\mbody(m,C,C) = (C,...)$ & & $\mbody(m,C,C) = \keyword{undefined}$ \\
		& & & & & \\
		& \multicolumn{1}{c}{\includegraphics[height=3cm]{pics/P4.pdf}} & &
		\multicolumn{1}{c}{\includegraphics[height=3cm]{pics/P5.pdf}} & & 
		\multicolumn{1}{c}{\includegraphics[height=3cm]{pics/P6.pdf}} \\ 
		(d) & $\mbody(m,T,T) = (T,...)$\ \ \  & (e) & $\mbody(m,T,T) = (T,...)$\ \ \ & (f) & $\mbody(m,C,T) = (C,...)$ \\
		& $\mbody(m,C,T) = \keyword{undefined}$ & & $\mbody(m,C,T) = \keyword{undefined}$ & & $\mbody(m,C,A) = (C,...)$ \\
		& $C\text{ rejected by type-check}$ & & $C\text{ rejected by type-check}$ & & $\mbody(m,C,B) = (C,...)$ \\
		& & & & & $\mbody(m,C,C) = (C,...)$
	\end{tabular}
	\caption{Examples on $\mbody$. ``$\uparrow$'' stands for hierarchical overriding.}\label{fig:examplesmbody}
	%\saveSpaceFig
\end{figure*}
